\begin{abstract}
We study reinforcement fine-tuning for mathematical reasoning, where
language models must produce not only correct answers but also
structurally coherent, multi-step reasoning traces. Existing
reinforcement learning with verifiable rewards (RLVR) approaches rely
predominantly on outcome-level signals---checking only whether the final
answer is correct---and ignore the \emph{topological quality} of the
intermediate reasoning process. This leads to three persistent problems:
(i)~outcome hacking, where models produce correct answers without sound
justification; (ii)~structural incoherence, where reasoning steps lack
logical dependency; and (iii)~long-chain redundancy, where unnecessarily
verbose traces waste inference budget and degrade accuracy.

We propose \textbf{TopoPRM} (\textbf{Topo}logy-aware \textbf{P}rocess
\textbf{R}eward \textbf{M}odel), a composite verifiable reward framework
that augments standard outcome rewards with two topology-aware process
signals. A \emph{topological structure reward} extracts the directed
acyclic graph (DAG) of reasoning steps and penalises cycles, orphan
nodes, and structural incoherence. A \emph{continuity reward} evaluates
step-to-step logical coherence, discouraging abrupt jumps within the
reasoning chain. To prevent reward hacking from auxiliary process signals,
we further introduce \emph{Stratified Clipping Advantage Estimation}
(SCAE), which hierarchically prioritises answer correctness over
structural quality during GRPO optimisation. We additionally propose a
\emph{reverse-KL distillation} stage that compresses the improved
reasoning behaviour from a 32B teacher into smaller student models.

Experiments on MATH500, GSM8K, CMATH, and GaoKao benchmarks show that
TopoPRM significantly improves both reasoning accuracy and structural
quality compared to outcome-only RLVR baselines, while the distilled
students retain the majority of gains at a fraction of the inference cost.
\end{abstract}
