\section{Conclusion}
\label{sec:conclusion}

We present TopoPRM, a topology-aware process reward framework for
reinforcement fine-tuning of mathematical reasoning models. TopoPRM
augments standard outcome rewards with two verifiable process signals: a
topological structure reward that evaluates whether the reasoning trace
forms a valid directed acyclic graph with acyclicity, connectivity, and
directional consistency, and a continuity reward that checks whether each
step follows from preceding context. Both signals are computed by
deterministic programs, keeping the method within the RLVR paradigm
without requiring learned reward models or human annotations. Stratified
Clipping Advantage Estimation (SCAE) prevents reward hacking by
hierarchically prioritizing answer correctness over auxiliary process
rewards. A reverse-KL distillation stage compresses these improvements
into smaller student models for efficient deployment. Experiments on
Chinese mathematical critique benchmarks show that TopoPRM improves
reasoning accuracy, particularly on harder problems, while producing
shorter and more structurally coherent reasoning chains compared to
outcome-only GRPO.

\paragraph{Limitations.}
Three limitations deserve attention. First, the DAG extraction relies on
rule-based parsing of inter-step references through keyword matching and
expression overlap. This procedure may miss implicit logical dependencies
that lack explicit surface-level cues, such as unstated algebraic
identities or geometric properties applied without reference. Second, the
continuity reward uses regex-based expression matching rather than
semantic understanding; it detects when a step references an expression
from a previous step but cannot identify subtle logical gaps or incorrect
applications of mathematical principles that reuse the same symbols.
Third, our evaluation focuses exclusively on mathematical reasoning in a
Chinese educational critique setting. Whether TopoPRM generalizes to
other structured reasoning domains, such as code generation or scientific
reasoning, remains an open question.

\paragraph{Future work.}
Three concrete directions follow from this work. First, replacing the
rule-based DAG extractor with a lightweight learned parser could capture
implicit dependencies while remaining fast enough for online reward
computation during GRPO training. Second, combining the verifiable
structural rewards of TopoPRM with learned
PRMs~\citep{lightman2023lets} could provide complementary supervision:
structural rewards enforce global coherence while learned rewards capture
fine-grained step correctness. Third, extending the framework to
multi-modal mathematical reasoning, where diagrams and figures introduce
spatial dependency structures beyond text, would test the generality of
topology-aware rewards in richer settings.
