\section{Experiments}
\label{sec:experiments}

\subsection{Experimental Setup}
\label{sec:setup}

\paragraph{Base model and training.}
We use Qwen3-32B~\citep{qwen3} as the base model. All training is
conducted using MS-Swift~\citep{msswift} with LoRA (rank 64, alpha 128)
applied to all linear layers. SFT uses 5{,}000 samples mixing 637
Chinese mathematical critique samples with 3{,}000 NuminaMath-CoT and
2{,}000 MetaMathQA English samples. GRPO uses 637 Chinese mathematical
critique prompts with TopoPRM composite rewards. We adopt the
MS-Swift~\citep{msswift} framework with its \emph{server-mode} GRPO
paradigm: a vLLM rollout server (4 GPUs, tensor-parallel) generates
completions, while 4 separate GPUs perform LoRA training. This
architecture cleanly separates inference and optimisation, enabling
high-throughput generation without memory conflicts. All experiments run
on 8$\times$ NVIDIA L20X GPUs (143\,GB each) with bfloat16 precision.
Detailed hyperparameters are in Appendix~\ref{app:details}.

\paragraph{Benchmarks.}
We evaluate on two Chinese math critique test sets: a \emph{Middle School}
set (2{,}181 samples) and a \emph{High School} set (5{,}414 samples),
totalling 7{,}595 evaluation samples. These test sets require the model
to critique student solutions, identify errors, and produce structured
scores---a task that demands both mathematical reasoning and precise
output formatting. We report \emph{Critique Accuracy} (exact score
match), \emph{Format Compliance} (\texttt{<think>} +
\texttt{<answer>} with valid JSON), and \emph{Average Length}
(in characters).

\paragraph{Baselines.}
We compare against the base Qwen3-32B, Qwen3-32B-Instruct, our SFT
checkpoint, and GRPO with outcome-only reward. We additionally evaluate
ablation variants that remove individual reward components.

\subsection{Main Results}
\label{sec:main_results}

\input{tables/main_results}

Table~\ref{tab:main_results} presents the main results. TopoPRM
(GRPO with full composite reward) consistently outperforms the SFT
baseline and outcome-only GRPO across both test sets. The improvements
are particularly pronounced on the harder High School set, suggesting
that topology-aware process rewards provide stronger guidance for complex
multi-step reasoning.

\subsection{Ablation Study}
\label{sec:ablation}

\input{tables/ablation_reward}

Table~\ref{tab:ablation_reward} shows the contribution of each reward
component. Removing the topological structure reward leads to the largest
accuracy drop, confirming that DAG-level structural verification is the
most impactful process signal. Removing the continuity reward also
degrades performance, though to a lesser extent.

\subsection{Structural Quality Analysis}
\label{sec:structural_quality}

\input{tables/structural_metrics}

Table~\ref{tab:structural_metrics} reports structural metrics of the
generated reasoning traces. GRPO with TopoPRM significantly improves
DAG acyclicity, reduces orphan conclusions, and increases step-to-step
continuity compared to SFT and outcome-only baselines. These results
confirm that the topological rewards effectively guide the model toward
producing more logically coherent reasoning structures.

\subsection{Length Analysis}
\label{sec:length_analysis}

\input{tables/ablation_length}

Table~\ref{tab:ablation_length} analyses the accuracy--length trade-off.
TopoPRM produces shorter reasoning traces than outcome-only GRPO while
maintaining higher accuracy, demonstrating that topology-aware rewards
naturally encourage more concise reasoning by penalising redundant
branches and orphan conclusions.

\subsection{Reasoning Compression}
\label{sec:compression_results}

\input{tables/compression}

Table~\ref{tab:compression} presents distillation results. The 14B
student retains the majority of the 32B teacher's accuracy while the 7B
student achieves competitive performance at significantly reduced
inference cost, validating the effectiveness of reverse-KL distillation
for transferring topologically coherent reasoning patterns.
