\section{Introduction}
\label{sec:introduction}

Mathematical reasoning requires language models to produce not merely
correct final answers but logically sound, step-by-step derivations in
which each conclusion follows from its
premises~\citep{ElKishky2024OpenAIOS,Chen2025TowardsRE}. Reinforcement
learning with verifiable rewards
(RLVR)~\citep{deepseekr1,shao2024deepseekmath} has become a standard
approach for improving such reasoning: a programmatic check verifies
whether the model's answer matches the ground truth, and the resulting
binary signal drives policy optimization through Group Relative Policy
Optimization (GRPO). Because the reward depends only on the final answer,
however, RLVR provides no gradient for improving the quality of the
reasoning trace itself.

This outcome-only supervision creates three systematic failure modes.
First, models can reach correct answers without constructing logically
sound derivations, a phenomenon sometimes called outcome
hacking~\citep{Denison2024SycophancyTS}. Second, reasoning traces often
contain orphan conclusions that lack supporting premises, circular
references between steps, and inconsistent logical direction, because
inter-step dependencies are never supervised. Third, without any length
or coherence signal, models tend to produce verbose, repetitive chains
that waste inference budget and occasionally introduce
self-contradictions~\citep{reasoning_compression_2025}.

Process reward models (PRMs)~\citep{lightman2023lets,wang2024math}
address some of these issues by assigning per-step scores, but they
require either expensive human annotations or learned verifiers whose
accuracy is itself uncertain. We observe that a complementary source of
process supervision is already present in the reasoning trace: the
\emph{topological structure} of inter-step dependencies. Mathematical
derivations form a directed acyclic graph (DAG) in which each step
depends on a subset of previous steps. Structural properties of this
graph, such as acyclicity, connectivity, and directional consistency, are
checkable by simple algorithms and provide verifiable process rewards
without any learned component.

We propose \textbf{TopoPRM}, a composite reward framework that
supplements the outcome reward with two topology-aware process signals.
Given a model-generated reasoning trace, a rule-based parser segments it
into steps and detects inter-step dependencies through shared
mathematical expressions, producing the implicit reasoning DAG. A
\emph{topological structure reward} evaluates whether this DAG satisfies
structural soundness properties. A \emph{continuity reward} checks
whether each step can be derived from preceding context, penalizing
unsupported jumps. Both rewards are computed by deterministic programs
and stay within the RLVR paradigm.

Combining multiple reward components introduces a new risk: the model
may optimize auxiliary process rewards at the expense of answer
correctness. To prevent this, we introduce \emph{Stratified Clipping
Advantage Estimation} (SCAE), which partitions each group of sampled
completions into correct and incorrect sets before computing advantages.
SCAE ensures that correct completions always receive positive advantages
regardless of their structural scores, while incorrect completions
receive negative advantages regardless of how well-structured they are.
After GRPO training, a reverse-KL distillation stage compresses the
improved reasoning behavior from the 32B teacher into smaller student
models.

\paragraph{Contributions.}
\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item We propose TopoPRM, a verifiable process reward that evaluates
    the topological structure of reasoning DAGs using deterministic
    algorithms, requiring no learned reward model or human annotations.

    \item We design Stratified Clipping Advantage Estimation (SCAE), a
    principled mechanism that prevents reward hacking when combining
    outcome and process rewards by hierarchically separating correct and
    incorrect completions during advantage computation.

    \item We implement a complete GRPO training pipeline within the
    MS-Swift framework, combining outcome, topological structure,
    continuity, format, and length rewards, all computed programmatically.

    \item We conduct experiments on 7{,}595 Chinese mathematical critique
    problems showing that TopoPRM improves both accuracy and structural
    coherence while producing shorter reasoning traces than outcome-only
    GRPO.
\end{enumerate}
