\section{Related Work}
\label{sec:related_work}

\paragraph{Reinforcement learning with verifiable rewards.}
RLHF~\citep{ouyang2022training} aligns language models with human
preferences through learned reward models trained on preference
annotations. DeepSeek-R1~\citep{deepseekr1} and
DeepSeekMath~\citep{shao2024deepseekmath} replaced learned preference
models with programmatic correctness checks, establishing the
reinforcement learning with verifiable rewards (RLVR) paradigm for
mathematical reasoning. GRPO~\citep{shao2024deepseekmath} computes
group-relative advantages without a separate critic network, reducing
memory cost relative to PPO while maintaining competitive performance on
math benchmarks. These methods supervise only the final answer and treat
the intermediate reasoning trace as opaque. TopoPRM retains the
verifiable reward paradigm but extends it to process-level supervision:
the topology and continuity rewards are computed by deterministic
programs, yet they provide step-level structural feedback that
outcome-only RLVR cannot offer.

\paragraph{Process reward models.}
\citet{lightman2023lets} introduced process reward models (PRMs) that
assign scalar rewards to individual reasoning steps, using human
annotations of step-level correctness as training signal.
Math-Shepherd~\citep{wang2024math} reduces annotation cost by estimating
step-level value through Monte Carlo rollouts from each intermediate
state. Proof-RM~\citep{proofRM2026} targets mathematical proofs and
designs reward functions that account for proof structure. These
approaches improve over outcome-only supervision but depend on either
expensive per-step human labels or learned verifiers whose accuracy is
itself uncertain. TopoPRM takes a complementary approach: rather than
scoring individual steps, it extracts structural properties of the full
reasoning graph (acyclicity, connectivity, directional consistency) using
deterministic rules, requiring no annotations and introducing no
additional model parameters.

\paragraph{Graph-structured reasoning.}
Graph-of-Thought~\citep{besta2024graph} organizes LLM reasoning into
graph structures through prompt engineering, enabling exploration of
multiple reasoning paths during inference.
GRP~\citep{grp2025} trains models to produce graph-structured outputs
with explicit cognitive labels, requiring specialized output formats and
task-specific decoding procedures. TopoPRM differs from both approaches
in a key respect: it uses graph topology as a \emph{reward signal} for
standard autoregressive generation rather than requiring models to
produce explicit graph-structured outputs. The model generates ordinary
text; our reward function extracts and evaluates the implicit dependency
graph post-hoc. This design requires no changes to model architecture or
output format, making it compatible with any text-generation policy.

\paragraph{Reward hacking and reasoning compression.}
Reward hacking, where models exploit auxiliary reward signals without
genuine task improvement, is a persistent problem in RL-based
training~\citep{Denison2024SycophancyTS}. In the GRPO setting,
DAPO~\citep{dapo2026} introduces dynamic sampling to stabilize training,
and difficulty-aware GRPO~\citep{difficultyGRPO2026} adjusts
optimization pressure based on problem difficulty. On the compression
side, on-policy self-distillation~\citep{reasoning_compression_2025} and
reverse-KL distillation~\citep{hinton2015distilling} reduce verbose
chain-of-thought outputs into shorter reasoning traces. TopoPRM
addresses reward hacking through a different mechanism: Stratified
Clipping Advantage Estimation (SCAE) hierarchically prioritizes answer
correctness over auxiliary process rewards, preventing models from
accumulating topology or continuity reward at the expense of accuracy.
Our distillation stage then transfers both accuracy and structural
conciseness from the TopoPRM-trained teacher to smaller student models.
