\documentclass{article}

\usepackage[preprint]{neurips_2025}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{dsfont}
\usepackage{listings}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  backgroundcolor=\color{gray!5},
}

\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\etc}{\textit{etc.}}
\newcommand{\cf}{\textit{cf.}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\title{TopoPRM: Topology-Aware Process Reward for\\Verifiable Mathematical Reasoning}

\author{
  Weilin Ruan\thanks{Equal contribution.} \\
  \And
  Author Two\footnotemark[1] \\
  \And
  Author Three \\
}

\begin{document}

\maketitle

\input{sections/abstract}
\input{sections/introduction}
\input{sections/related_work}
\input{sections/method}
\input{sections/experiments}
\input{sections/conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\appendix
\section{Training Details}
\label{app:details}

\paragraph{SFT stage.}
We fine-tune Qwen3-32B using LoRA with rank 64 and alpha 128 on all
linear layers. The SFT dataset consists of 5{,}000 samples: 637 Chinese
mathematical critique examples and 4{,}363 English math reasoning problems
from NuminaMath-CoT and MetaMathQA. Training runs for 3 epochs (120
steps) with learning rate $5 \times 10^{-5}$, cosine decay with 3\%
warmup, batch size 2, gradient accumulation 8, and max sequence length
8{,}192. Final SFT loss: 0.311, token accuracy: 89.7\%.

\paragraph{GRPO stage.}
We train with the TopoPRM composite reward on 637 Chinese mathematical
critique prompts. Each prompt generates 8 completions with temperature
0.7, top-$p$ 0.95, and max completion length 2{,}048. We adopt
MS-Swift's \emph{server mode} architecture, where a dedicated vLLM
rollout server (4 GPUs, tensor-parallel) handles high-throughput
generation while 4 separate GPUs perform LoRA gradient updates. After
each optimisation step, updated adapter weights are synchronised back to
the server via NCCL broadcast, ensuring the generation policy stays
current. Training runs for 1 epoch with learning rate
$5 \times 10^{-6}$, cosine decay, per-device batch size 2, and gradient
accumulation 4.

\paragraph{Reward weights.}
Default weights: $w_o = 0.4$ (outcome), $w_t = 0.2$ (topology),
$w_c = 0.15$ (continuity), $w_f = 0.15$ (format), $w_l = 0.1$ (length).

\paragraph{Hardware.}
All experiments run on 8$\times$ NVIDIA L20X GPUs (143\,GB VRAM each).
For GRPO, we partition GPUs into an inference group (4 GPUs running the
vLLM rollout server with tensor parallelism) and a training group
(4 GPUs running distributed LoRA optimisation), following the
MS-Swift~\citep{msswift} framework's recommended server-mode paradigm.

\section{Case Study}
\label{app:case_study}

We present a representative example comparing SFT, outcome-only GRPO,
and TopoPRM outputs on a High School algebra problem. The problem
requires setting up and solving a system of equations from a word problem.

\paragraph{SFT output.}
The SFT model produces a correct answer but with redundant intermediate
steps and one orphan conclusion that does not connect to the main
derivation chain. The reasoning DAG contains a back-edge from the
conclusion to an earlier auxiliary step, violating acyclicity.

\paragraph{Outcome-only GRPO output.}
The outcome-only model reaches the correct answer more concisely but
skips a key substitution step, producing a reasoning trace with a
continuity gap. The topological structure reward would assign a low
continuity score to this trace.

\paragraph{TopoPRM output.}
The TopoPRM model produces a concise, well-structured derivation where
each step logically follows from its predecessors. The extracted DAG is
acyclic, fully connected, and directionally consistent. The reasoning
trace is 23\% shorter than the SFT output while maintaining correctness.

% Detailed examples with actual model outputs will be included after
% training completes and representative samples are selected.

\section{Reward Function Details}
\label{app:rewards}

\paragraph{Outcome reward.}
Parses the model's \texttt{<answer>} JSON to extract the predicted
student score and critique conclusion. Exact score match yields 1.0;
within $\pm 1$ yields 0.5. Matching the conclusion adds 0.5 bonus.
The total is capped and normalised to $[0, 1]$.

\paragraph{Format reward.}
Checks for \texttt{<think>$\cdots$</think>} and
\texttt{<answer>$\cdots$</answer>} blocks with valid JSON:
both present $\to$ 1.0; only valid \texttt{<answer>} $\to$ 0.3;
otherwise $\to$ 0.0.

\paragraph{Length reward.}
Linear decay from 1.0 (at $\leq$ 2{,}000 characters) to 0.0 (at
$\geq$ 4{,}000 characters).

\paragraph{Topological structure reward.}
Defined in \S\ref{sec:r_topo}. The DAG extraction uses rule-based step
segmentation (numbered steps, mathematical delimiters, logical
connectives) and dependency detection (shared mathematical expressions,
variable references).

\paragraph{Continuity reward.}
Defined in \S\ref{sec:r_cont}. Uses regex-based expression matching
to verify that each step references expressions or claims from prior
steps or the problem statement.

\section{Additional Results}
\label{app:additional}
% Training curves, per-category breakdowns, and additional ablations
% will be added after all experiments complete.

\end{document}
